Pre-Analysis Plan: Bend or Break? Experimental Evidence of Voters' Punishment for Striking Political Compromises

### 2021-04-22 docs/pap/compromise-punishment-pap.Rmd
update pap

---
title: "Pre-Analysis Plan: Who Bends and Who Breaks? Experimental Evidence for Conditions Affecting Voters' Evaluations of Politicians Striking Compromises"
date: "`r format(Sys.time(), '%d %B, %Y - %X (%Z)')`"
output: 
  pdf_document:
    toc: yes
    number_sections: true
editor_options: 
  chunk_output_type: console
bibliography: references.bib
urlcolor: blue
linkcolor: blue
header-includes:
   - \usepackage{floatrow}
   - \floatsetup[figure]{capposition=top}
   - \floatsetup[table]{capposition=top}
   - \usepackage{booktabs}
   - \usepackage{longtable}
   - \usepackage{array}
   - \usepackage{multirow}
   - \usepackage{wrapfig}
   - \usepackage{float}
   - \usepackage{colortbl}
   - \usepackage{pdflscape}
   - \usepackage{tabu}
   - \usepackage{threeparttable}
   - \usepackage{threeparttablex}
   - \usepackage[normalem]{ulem}
   - \usepackage{makecell}
   - \usepackage{xcolor}
---
```{r setup, include=FALSE}
## include this at top of your RMarkdown file for pretty output
## make sure to have the printr package installed: install.packages('printr')
knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE)
#library(printr)
library(tidyverse)
library(kableExtra)
options(kableExtra.latex.load_packages = FALSE)
```

@@

```{r h1, eval = FALSE, echo = TRUE}
df <- d %>% select(PT1:PT4, gender, compromise)

depVarList <- setdiff(colnames(df), c("gender", "compromise"))
allModels <- lapply(depVarList, function(x){
  lm(formula= paste0("`", x, "` ~ gender * compromise"), 
     data= df, na.action = na.omit)})

for(i in 1:length(depVarList)){
  if(i==1){
    m <- summary(margins(allModels[[i]]), at = list(compromise = 1)) %>%
      filter(factor=="gender") %>%
      mutate(y = depVarList[i],
             lower = AME - (1.645 * SE),
             upper = AME + (1.645 * SE)) %>%
      select(AME, upper, lower, y)

  }
  else{
    tmp <- summary(margins(allModels[[i]]), at = list(compromise = 1)) %>%
      filter(factor=="gender") %>%
      mutate(y = depVarList[i],
             lower = AME - (1.645 * SE),
             upper = AME + (1.645 * SE)) %>%
      select(AME, upper, lower, y)
    m <- m %>%
      add_case(tmp)
  }
}
```

@@

depVarList <- setdiff(colnames(df), c("migration", "compromise"))
allModels <- lapply(depVarList, function(x){
  lm(formula= paste0("`", x, "` ~ migration * compromise"), 
     data= d, na.action = na.omit)})

for(i in 1:length(depVarList)){
  if(i==1){
    m <- summary(margins(allModels[[i]]), at = list(compromise = 1)) %>%
      filter(factor=="migration") %>%
      mutate(y = depVarList[i],
             lower = AME - (1.645 * SE),
             upper = AME + (1.645 * SE)) %>%
      select(AME, upper, lower, y)
  }
  else{
    tmp <- summary(margins(allModels[[i]]), at = list(compromise = 1)) %>%
      filter(factor=="migration") %>%
      mutate(y = depVarList[i],
             lower = AME - (1.645 * SE),
             upper = AME + (1.645 * SE)) %>%
      select(AME, upper, lower, y)
    m <- m %>%
      add_case(tmp)
  }
}
```

@@

depVarList <- setdiff(colnames(df), c("intersection", "compromise"))
allModels <- lapply(depVarList, function(x){
  lm(formula= paste0("`", x, "` ~ intersection * compromise"), 
     data= d, na.action = na.omit)})

for(i in 1:length(depVarList)){
  if(i==1){
    m <- summary(margins(allModels[[i]]), at = list(compromise = 1)) %>%
      filter(factor=="intersection") %>%
      mutate(y = depVarList[i],
             lower = AME - (1.645 * SE),
             upper = AME + (1.645 * SE)) %>%
      select(AME, upper, lower, y)
  }
  else{
    tmp <- summary(margins(allModels[[i]]), at = list(compromise = 1)) %>%
      filter(factor=="intersection") %>%
      mutate(y = depVarList[i],
             lower = AME - (1.645 * SE),
             upper = AME + (1.645 * SE)) %>%
      select(AME, upper, lower, y)
    m <- m %>%
      add_case(tmp)
  }
}
```

@@

>>>>

---
title: "Pre-Analysis Plan: Bend or Break? Experimental Evidence of Voters' Punishment for Striking Political Compromises"
date: "`r format(Sys.time(), '%d %B, %Y - %X (%Z)')`"
output: 
  pdf_document:
    toc: yes
    number_sections: true
editor_options: 
  chunk_output_type: console
bibliography: references.bib
urlcolor: blue
linkcolor: blue
header-includes:
   - \usepackage{floatrow}
   - \floatsetup[figure]{capposition=top}
   - \floatsetup[table]{capposition=top}
   - \usepackage{booktabs}
   - \usepackage{longtable}
   - \usepackage{array}
   - \usepackage{multirow}
   - \usepackage{wrapfig}
   - \usepackage{float}
   - \usepackage{colortbl}
   - \usepackage{pdflscape}
   - \usepackage{tabu}
   - \usepackage{threeparttable}
   - \usepackage{threeparttablex}
   - \usepackage[normalem]{ulem}
   - \usepackage{makecell}
   - \usepackage{xcolor}
---
```{r setup, include=FALSE}
## include this at top of your RMarkdown file for pretty output
## make sure to have the printr package installed: install.packages('printr')
knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE)
#library(printr)
library(tidyverse)
library(kableExtra)
options(kableExtra.latex.load_packages = FALSE)
```

@@

```{r h1, eval = FALSE, echo = TRUE}
source(here::here("src/lib/functions.R"))

df <- d %>% select(PT1:PT4, gender, compromise)
h1 <- regression(data = df, a = gender, b = compromise)
```

@@

h2 <- regression(data = df, a = migration, b = compromise)
```

@@

h3 <- regression(data = df, a = intersection, b = compromise)
```

@@

```{r pooled, echo = TRUE, eval = FALSE}
h3_p <- pooled_regression(data = df, a = intersection, b = compromise, c = issues)
```
